Time for a rethink: disparity-through-time

### 2017-12-11 manuscript/time-slice.tex
Added outline figure first try + answers to comments

% However, our methods for analysing diversity-through-time have not changed all that much in the XX years they have been popular. %TG: small caveat on that after litterature search for the disparity review paper: disparity-through-time analysis have not changed much since Foote 1992, Foote and Gould 1992 and Briggs et al. 1992 in the classic palaeobiology appro,ach...
%TG: However to not piss of people, there were several attempts to "rationalise" (Wills 2001), test (Ciampaglio 2001) and expand (Pavlinov 2011 and Gerber et al 2011) namely with univariate approaches and "dtt" analysis (Harmon et al 2003).
%TG: One of the critisisms from one of the rude reviews was this idea that age of popular method has nothing to do with its performance, by nuancing this sentence we can basically say: yeah, some people have made great advances and proposed great ideas for CORRECTING ERRORS in the methods from the 90s but somehow everybody have ignored them (in palaeobiology).
% NC: OK so lets save ourselves some pain and not mention this at all and save it all for the bitching in the review paper!!!

@@

% NC: might move this to the NHM github account

% Add overview figure

  %\begin{figure}[!htbp]
    %\centering
    %\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/overview}
    %\caption[caption title]
    % {caption text}
    %\label{overview}
  %\end{figure}

@@

    \item The ``gradual splits'' model (probabilistic), selects the ordination score from both the ancestor and the descendant with a probability equal to the distance between the slice.
    % NC: I'm unsure what you mean here: "the distance between the slice." Do you mean the branch length, the interval between slices, or the distance between the slice and the node?
          \begin{equation}
              p(\text{ancestor}) = \frac{d(\text{ancestor},\text{slice})}{d(\text{ancestor},\text{descendant})}
          \end{equation}
          \begin{equation}
              p(\text{descendant}) = 1 - p(\text{ancestor})
          \end{equation}
    \noindent Where $d(x,y)$ is the distance measured as branch length.
    \end{enumerate}

>>>>

% However, our methods for analysing diversity-through-time have not changed all that much in the XX years they have been popular. %TG: small caveat on that after litterature search for the disparity review paper: disparity-through-time analysis have not changed much since Foote 1992, Foote and Gould 1992 and Briggs et al. 1992 in the classic palaeobiology appro,ach...
%TG: However to not piss of people, there were several attempts to "rationalise" (Wills 2001), test (Ciampaglio 2001) and expand (Pavlinov 2011 and Gerber et al 2011) namely with univariate approaches and "dtt" analysis (Harmon et al 2003).
%TG: One of the critisisms from one of the rude reviews was this idea that age of popular method has nothing to do with its performance, by nuancing this sentence we can basically say: yeah, some people have made great advances and proposed great ideas for CORRECTING ERRORS in the methods from the 90s but somehow everybody have ignored them (in palaeobiology).
% NC: OK so lets save ourselves some pain and not mention this at all and save it all for the bitching in the review paper!!!
% TG: agree!

@@

% NC: might move this to the NHM github account
% TG: why that? It'll be just extra hassle no?

% Add overview figure
%TG: This is a first draft of the figure and its caption. Tell me what you think.

  \begin{figure}[!htbp]
    \centering
    \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{outlinesvg.pdf}
    \caption[caption title]
    {Outline of the disparity-through-time pipeline applied to each data set: 1) we used ancestral characters estimation to infer nodal character states, 2) we measured the pairwise Gower distance between the tips and nodal characters, 3) we ordinated the distance matrix using a PCoA, 4) we split that matrix using stratigraphy bins, equal bins and the time slice method, 5) we measured disparity through time for each of these methods.}
    \label{overview}
  \end{figure}

@@

    \item The ``gradual splits'' model (probabilistic), selects the ordination score from both the ancestor and the descendant with a probability function of the distance between the nodes/tips and the slice.
    % NC: I'm unsure what you mean here: "the distance between the slice." Do you mean the branch length, the interval between slices, or the distance between the slice and the node?
    %TG: I've clarified as above. Tell me if it's clearer. In my words: the distance between the slice and the node, like you illustrate in your presentation (nicely done by the way!)
          \begin{equation}
              p(\text{ancestor}) = \frac{d(\text{ancestor},\text{slice})}{d(\text{ancestor},\text{descendant})}
          \end{equation}
          \begin{equation}
              p(\text{descendant}) = 1 - p(\text{ancestor})
          \end{equation}
    \noindent Where $d(x,y)$ is the distance measured as branch length.
    \end{enumerate}
